Gsmodutils: A python based framework for test driven genome scale metabolic model development

### 2017-12-11 article/article.tex
minor changes to article

The iCac 967 model presents a smaller set of changes to the annotation of the \textit{C. acetobutylicum} model.
While the number of genes increased from 802 to 967 manual annotation actually reduced the number of reactions and metabolites from 1462 to 1137 and 1231 to 1058, respectively.
The annotation ane experimental evidence from iCac802 \cite{dash2014capturing} to iCac967 \cite{yoo2015quantitative} is greatly expanded.
However, it is not entirely clear, from the initial publication, the extent to which the expanded iCaC907 model preserves crucial experimental validation.
The following sections aim to check the later model against previous validation criteria.

@@

In addition, a design listing the constraints changed in model version iCaC907 
\footnote{We would like to note that such a significant change to a model, in many practical cases, would not be considered a design but, rather, a separate model.
Separate models within the same project is a feature supported by gsmodutils.}.
\\
\textbf{Model comparison: TODO Diffs between existing models - use (and further develop) gsmodutils diff for model stats}.

@@

\section*{Acknowledgements}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work, Rupert Norman for assistance testing and forming the idea of this software and Thomas Millat for crucial scientific advice.

>>>>

The iCac 967 model presents a smaller set of changes to the annotation of the \textit{C. acetobutylicum} model.
While the number of genes increased from 802 to 967 manual annotation actually reduced the number of reactions and metabolites from 1462 to 1137 and 1231 to 1058, respectively.
The annotation ane experimental evidence from iCac802 \cite{dash2014capturing} to iCac967 \cite{yoo2015quantitative} is greatly expanded.
However, it is not entirely clear, from the initial publication, the extent to which the expanded iCaC967 model preserves crucial experimental validation.
The following sections aim to check the later model against previous validation criteria.

@@

In addition, a design listing the constraints changed in model version iCaC967 
\footnote{We would like to note that such a significant change to a model, in many practical cases, would not be considered a design but, rather, a separate model.
Separate models within the same project is a feature supported by gsmodutils.}.
\\
\textbf{Model comparison: TODO Diffs between existing models - use (and further develop) gsmodutils diff for model stats}.

@@

\section*{Acknowledgements}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work, Rupert Norman for assistance testing and forming the idea of this software, Thomas Millat for crucial scientific advice and Phillipe Soucaille for assistance reconstructing the iCac967
